---
title: "Clustering Algorithms"
author: "Ekim Buyuk"
date: "12/3/2018"
output: html_document
---

#Creation of New Dataframes For Part I of Doggo To Human Match:

# Dataframe 1: House + Cold Weather + New Owner Doggos
```{r}
final_stars_data <- rownames_to_column(final_stars_data,"Doggo")

data1 <- final_stars_data %>% 
  filter(GoodForNoviceOwners == 2 | GoodForNoviceOwners == 3 | GoodForNoviceOwners == 4) %>% 
  filter(ToleratesColdWeather == 2 | ToleratesColdWeather == 3 | ToleratesColdWeather == 4)

data1 <- data1 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data1 <- column_to_rownames(data1,"Doggo")
```

# Dataframe 2: House + Hot Weather + New Owner Doggos
```{r}
data2 <- final_stars_data %>% 
  filter(GoodForNoviceOwners == 2 | GoodForNoviceOwners == 3 | GoodForNoviceOwners == 4) %>% 
  filter(ToleratesHotWeather == 2 | ToleratesHotWeather == 3 | ToleratesHotWeather == 4)

data2 <- data2 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data2 <- column_to_rownames(data2,"Doggo")
```

# Dataframe 3: House + Cold Weather + Old Owner Doggos
```{r}
data3 <- final_stars_data %>% 
  filter(ToleratesColdWeather == 2 | ToleratesColdWeather == 3 | ToleratesColdWeather == 4)

data3 <- data3 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data3 <- column_to_rownames(data3,"Doggo")
```

# Dataframe 4: House + Hot Weather + Old Owner Doggos
```{r}
data4 <- final_stars_data %>%
  filter(ToleratesHotWeather == 2 | ToleratesHotWeather == 3 | ToleratesHotWeather == 4)

data4 <- data4 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data4 <- column_to_rownames(data4,"Doggo")
```

# Dataframe 5: Apartment/Dorm + Hot Weather + New Owner Doggos
```{r}
data5 <- final_stars_data %>% 
  filter(AdaptsWelltoApartmentLiving == 2 | AdaptsWelltoApartmentLiving == 3 | AdaptsWelltoApartmentLiving == 4) %>%
  filter(GoodForNoviceOwners == 2 | GoodForNoviceOwners == 3 | GoodForNoviceOwners == 4) %>% 
  filter(ToleratesHotWeather == 2 | ToleratesHotWeather == 3 | ToleratesHotWeather == 4)

data5 <- data5 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data5 <- column_to_rownames(data5,"Doggo")
```

# Dataframe 6: Apartment/Dorm + Cold Weather + New Owner Doggos
```{r}
data6 <- final_stars_data %>% 
  filter(AdaptsWelltoApartmentLiving == 2 | AdaptsWelltoApartmentLiving == 3 | AdaptsWelltoApartmentLiving == 4) %>%
  filter(GoodForNoviceOwners == 2 | GoodForNoviceOwners == 3 | GoodForNoviceOwners == 4) %>% 
  filter(ToleratesColdWeather == 2 | ToleratesColdWeather == 3 | ToleratesColdWeather == 4)

data6 <- data6 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data6 <- column_to_rownames(data6,"Doggo")
```

# Dataframe 7: Apartment/Dorm + Hot Weather + Old Owner Doggos
```{r}
data7 <- final_stars_data %>% 
  filter(AdaptsWelltoApartmentLiving == 2 | AdaptsWelltoApartmentLiving == 3 | AdaptsWelltoApartmentLiving == 4) %>%
  filter(ToleratesHotWeather == 2 | ToleratesHotWeather == 3 | ToleratesHotWeather == 4)

data7 <- data7 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data7 <- column_to_rownames(data7,"Doggo")
```

# Dataframe 8: Apartment/Dorm + Cold Weather + Old Owner Doggos
```{r}
data8 <- final_stars_data %>% 
  filter(AdaptsWelltoApartmentLiving == 2 | AdaptsWelltoApartmentLiving == 3 | AdaptsWelltoApartmentLiving == 4) %>%
  filter(ToleratesColdWeather == 2 | ToleratesColdWeather == 3 | ToleratesColdWeather == 4)

data8 <- data8 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data8 <- column_to_rownames(data8,"Doggo")
```

#Dataframe 9: House + Normal Weather + Old Owner
```{r}
data9 <- final_stars_data %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data9 <- column_to_rownames(data9,"Doggo")
```

#Dataframe 10: House + Normal Weather + New Owner

```{r}
data10 <- final_stars_data %>% 
  filter(GoodForNoviceOwners == 2 | GoodForNoviceOwners == 3 | GoodForNoviceOwners == 4)

data10 <- data10 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data10 <- column_to_rownames(data10,"Doggo")
```

#Dataframe 11: Apartment/Dorm + Normal Weather + Old Owner
```{r}
data11 <- final_stars_data %>% 
  filter(AdaptsWelltoApartmentLiving == 2 | AdaptsWelltoApartmentLiving == 3 | AdaptsWelltoApartmentLiving == 4)

data11 <- data11 %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data11 <- column_to_rownames(data11,"Doggo")
```

#Dataframe 12: Apartment/Dorm + Normal Weather + New Owner
```{r}
data12 <- final_stars_data %>% 
  filter(GoodForNoviceOwners == 2 | GoodForNoviceOwners == 3 | GoodForNoviceOwners == 4) %>%
  filter(AdaptsWelltoApartmentLiving == 2 | AdaptsWelltoApartmentLiving == 3 | AdaptsWelltoApartmentLiving == 4)

data12 <- final_stars_data %>%
  select(Doggo,AffectionatewithFamily,IncrediblyKidFriendlyDogs,DogFriendly,FriendlyTowardStrangers,Intensity,EnergyLevel,PotentialForPlayfulness,EasyToTrain,WanderlustPotential)
data12 <- column_to_rownames(data12,"Doggo")
```

#Mixed Membership Clustering Alogorithm

```{r}
mixedMemfunction = function(Total, J, K, dataset) {
  Rj <- rep(1, J)
  Nijr <- array(1, dim = c(Total, J, max(Rj))) #multinomial so rank is 1 for each
  Vj <- rep(5, J) #5 choices for each variable 
  alpha <- rep(.2, K) #initalize alpha to .2
  dist <- rep("multinomial", J) #all variables are multinomial 
  obs <- array(0, dim = c(Total, J, max(Rj), max(Nijr)))
  obs[, , 1, 1] <- as.matrix(dataset)
  set.seed(112718)
  theta <- array(0, dim = c(J, K, max(Vj))) 
  for (j in 1:J) {
    theta[j, , ] <- gtools::rdirichlet(K, rep(.8, Vj[j])) 
  }
  initial <- mixedMemModel(Total = Total, J = J, Rj = Rj,
                         Nijr = Nijr, K = K, Vj = Vj, alpha = alpha,
                         theta = theta, dist = dist, obs = obs)
  computeELBO(initial)
  st = proc.time()
  out <- mmVarFit(initial, printStatus = 1, printMod = 25)
  lambda.point <- out$phi / rowSums(out$phi)
  new_data1 = list()
  
  for (i in 1:K) {
    popAgree <- out$theta[, i, 1]
    new_data1[[i]] <- popAgree 
  }
  
  new_groups <- as.data.frame(new_data1)
  rownames(new_groups) <- colnames(dataset)
  colnames(new_groups) <- as.vector(1:K)
  new_groups <- rownames_to_column(new_groups, "Variable")
  
  new_groups_t = as.data.frame(t(new_groups),stringsAsFactors = FALSE)
  colnames(new_groups_t) <- as.character(unlist(new_groups_t[1,]))
  new_data1 = new_groups_t[-1, ] 
  new_data1$AffectionatewithFamily <- as.numeric(new_data1$AffectionatewithFamily)
  new_data1$IncrediblyKidFriendlyDogs <-as.numeric(new_data1$IncrediblyKidFriendlyDogs)
  new_data1$DogFriendly <-as.numeric(new_data1$DogFriendly)
  new_data1$FriendlyTowardStrangers <-as.numeric(new_data1$FriendlyTowardStrangers)
  new_data1$Intensity <-as.numeric(new_data1$Intensity)
  new_data1$EasyToTrain <-as.numeric(new_data1$EasyToTrain)
  new_data1$PotentialForPlayfulness <-as.numeric(new_data1$PotentialForPlayfulness)
  new_data1$EnergyLevel <-as.numeric(new_data1$EnergyLevel)
  new_data1$WanderlustPotential <-as.numeric(new_data1$WanderlustPotential)
  
  for (i in 1:K) {
    new_data1$FriendlinessScore[i] <- sum(as.numeric(new_data1$AffectionatewithFamily[i]),new_data1$IncrediblyKidFriendlyDogs[i],new_data1$IncrediblyKidFriendlyDogs[i],new_data1$FriendlyTowardStrangers[i])
    new_data1$PlayScore[i] <- sum(new_data1$PotentialForPlayfulness[i],new_data1$EnergyLevel[i])
    new_data1$IndependenceScore[i] <- sum(new_data1$EasyToTrain[i], new_data1$WanderlustPotential)
}

  new_data1 <- rownames_to_column(new_data1, "Variable")

  indiv_in_cluster <- as.data.frame(lambda.point)
  rownames(indiv_in_cluster) <- rownames(data1)
  colnames(indiv_in_cluster) <- 1:K
  indiv_in_cluster <- rownames_to_column(indiv_in_cluster,"Variable")
  
  return(list(new_data1,indiv_in_cluster))
}

test = mixedMemfunction(Total = nrow(data1),J = length(data1), K = round(nrow(data1)/10,0),dataset = data1)
test[[1]]
  
#Get the values for tendencies for each group:
new_data1 = list()
for (i in 1:20) {
  popAgree <- out$theta[, i, 1]
  new_data1[[i]] <- popAgree 
}

new_groups <- as.data.frame(new_data1)
rownames(new_groups) <- colnames(new_data)
colnames(new_groups) <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)

lambda.point <- out$phi / rowSums(out$phi)
test <- as.data.frame(lambda.point)
rownames(test) <- rownames(new_data)
colnames(test) <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)

new_groups <- add_rownames(new_groups, "Variable")

importance = "cuddliness"

options(scipen = 999)
test = as.data.frame(t(new_groups),stringsAsFactors = FALSE)
colnames(test) <- as.character(unlist(test[1,]))
new_data1 = test[-1, ] 
new_data1$AffectionatewithFamily <- as.numeric(new_data1$AffectionatewithFamily)
new_data1$IncrediblyKidFriendlyDogs <-as.numeric(new_data1$IncrediblyKidFriendlyDogs)
new_data1$DogFriendly <-as.numeric(new_data1$DogFriendly)
new_data1$FriendlyTowardStrangers <-as.numeric(new_data1$FriendlyTowardStrangers)
new_data1$Intensity <-as.numeric(new_data1$Intensity)
new_data1$EasyToTrain <-as.numeric(new_data1$EasyToTrain)
new_data1$PotentialForPlayfulness <-as.numeric(new_data1$PotentialForPlayfulness)
new_data1$EnergyLevel <-as.numeric(new_data1$EnergyLevel)
new_data1$WanderlustPotential <-as.numeric(new_data1$WanderlustPotential)

for (i in 1:20) {
  new_data1$FriendlinessScore[i] <- sum(as.numeric(new_data1$AffectionatewithFamily[i]),new_data1$IncrediblyKidFriendlyDogs[i],new_data$IncrediblyKidFriendlyDogs[i],new_data1$FriendlyTowardStrangers[i])
  new_data1$PlayScore[i] <- sum(new_data1$PotentialForPlayfulness[i],new_data1$EnergyLevel[i])
  new_data1$IndependenceScore[i] <- sum(new_data1$EasyToTrain[i], new_data1$WanderlustPotential)
}

new_data1 <- add_rownames(new_data1, "Variable")

importance = "train"
peers = "3"
energy = "1"
intense = "1"
if(importance == "train") {
  potential_groups <- new_data1 %>% filter(EasyTrainScore >= median(new_data1$EasyTrainScore))
  if(peers == 3 | peers == 4 | peers == 5) {
    potential_groups <- potential_groups %>% filter(DogFriendly >= median(potential_groups$DogFriendly))
    if(energy == 3 | energy == 4 | energy == 5) {
      potential_groups <- potential_groups %>% filter(EnergyLevel >= median(potential_groups$EnergyLevel))
      if(intense == 3 | intense == 4 | intense == 5) {
        cluster <- potential_groups %>% filter(Intensity >= median(potential_groups$Intensity))
        if(nrow(cluster) != 1) {
          cluster <- cluster[which.max(cluster$EasyTrainScore),]
        }
        cluster <- as.numeric(cluster[1,1])
      }
      if(intense == 1 | intense == 2) {
        cluster <- potential_groups %>% filter(Intensity >= median(potential_groups$Intensity))
        if(nrow(cluster) != 1) {
          cluster <- cluster[which.max(cluster$EasyTrainScore),]
        }
        cluster <- as.numeric(cluster[1,1])
      }
    }
    if(energy == 1 | energy == 2){
      potential_groups <- potential_groups %>% filter(EnergyLevel <= median(potential_groups$EnergyLevel))
      if(intense == 3 | intense == 4 | intense == 5) {
        cluster <- potential_groups %>% filter(Intensity >= median(potential_groups$Intensity))
        if(nrow(cluster) != 1) {
          cluster <- cluster[which.max(cluster$EasyTrainScore),]
        }
        cluster <- as.numeric(cluster[1,1])
      }
      if(intense == 1 | intense == 2) {
        cluster <- potential_groups %>% filter(Intensity >= median(potential_groups$Intensity))
        if(nrow(cluster) != 1) {
          cluster <- cluster[which.max(cluster$EasyTrainScore),]
        }
        cluster <- as.numeric(cluster[1,1])
      }
    }
  }
  if(peers == 1 | peers == 2) {
    potential_groups <- potential_groups %>% filter(DogFriendly <= median(potential_groups$DogFriendly))
    if(energy == 3 | energy == 4 | energy == 5) {
      potential_groups <- potential_groups %>% filter(EnergyLevel >= median(potential_groups$EnergyLevel))
      if(intense == 3 | intense == 4 | intense == 5) {
        cluster <- potential_groups %>% filter(Intensity >= median(potential_groups$Intensity))
        if(nrow(cluster) != 1) {
          cluster <- cluster[which.max(cluster$EasyTrainScore),]
        }
        cluster <- as.numeric(cluster[1,1])
      }
      if(intense == 1 | intense == 2) {
        cluster <- potential_groups %>% filter(Intensity >= median(potential_groups$Intensity))
        if(nrow(cluster) != 1) {
          cluster <- cluster[which.max(cluster$EasyTrainScore),]
        }
        cluster <- as.numeric(cluster[1,1])
      }
    }
    if(energy == 1 | energy == 2){
      potential_groups <- potential_groups %>% filter(EnergyLevel <= median(potential_groups$EnergyLevel))
      if(intense == 3 | intense == 4 | intense == 5) {
        cluster <- potential_groups %>% filter(Intensity >= median(potential_groups$Intensity))
        if(nrow(cluster) != 1) {
          cluster <- cluster[which.max(cluster$EasyTrainScore),]
        }
        cluster <- as.numeric(cluster[1,1])
      }
      if(intense == 1 | intense == 2) {
        cluster <- potential_groups %>% filter(Intensity >= median(potential_groups$Intensity))
        if(nrow(cluster) != 1) {
          cluster <- cluster[which.max(cluster$EasyTrainScore),]
        }
        cluster <- as.numeric(cluster[1,1])
      }
    }
  }
}

indiv_in_cluster <- as.data.frame(lambda.point)
rownames(indiv_in_cluster) <- rownames(final_stars_data)
colnames(indiv_in_cluster) <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)
indiv_in_cluster <- rownames_to_column(indiv_in_cluster)

colnames(indiv_in_cluster)[cluster+1] <- 'Win'
high_prob = indiv_in_cluster %>% filter(Win > 0.5)
if (nrow(high_prob) > 10) {
  backwards_ordered = high_prob[order(high_prob$Win),]
  high_prob <- backwards_ordered[tail(seq_along(backwards_ordered),10),]
}
doggos <- data_frame(Doggo = high_prob$rowname,
                     'Match Percentage' = paste0(round(high_prob$Win,4)*100,"%"),
                     )
```

